### 2014-08-31 fundamentals/qa.tex

\subsection{Testing}

@@

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this
coding style guides are the software analogy to the natural language ones, 
such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger2008google} for all software contributions.

>>>>

Sections \ref{sec:qa-testing}-\ref{sec:qa-ci} discuss in greater detail the software 
development components that comprise the cyclus verification strategy.
Each of these on its own is a valuable addition to QA but is cannot be the 
entire answer to the requirements imposed by NQA-1. Taken together and strictly 
adhered to they present a fortress through which undeisrable code may siege, 
but never take.

\subsection{Testing}
\label{sec:qa-testing}

@@

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this
coding style guides are the software analogy to the natural language ones, 
such as the Chicago Manual of Style. Cyclus strictly enforces the use of the 
Google C++ Style Guide \cite{weinberger2008google} for all software contributions.
This means that all developers of cyclus nominally write cyclus code in the same 
way.  This homogenization may be a hurdle to new developers but ultimately 
makes the it much more legible. Adoption of a single style guide also settles
timeless arguments over what style is `the best.' Having only one means that 
there is a common enemy for all developers to dislike equally.

\subsection{Continuous Integration}
\label{sec:qa-ci}

Continuous integration (CI) the idea that software should be tested and validated 
as it is being developed, rather than as a final stage in a longer development 
cycle.  Under CI every pull request is tested independently immeadiately after 
it is proposed. Such tests shoudl be run on all officially supported platforms. 
Cyclus uses a CI platform called Polyphemus \cite{polyphemus_2014}.

Polyphemus serves as an intermediary between GitHub pull requests on the frontend 
and temporary cyclus servers on the backend. These servers are hosted by 
the Build \& Test Laboratory (BaTLab) \cite{batlab_2014} at the University of 
Wisconsin-Madison. Whenever a pull request is created, Polyphemus performs 
the following actions:

\begin{enumerate}
    \item Copies cyclus with the pull requested code to BaTLab,
    \item Initiliazes Linux and Mac OSX servers,
    \item Builds cyclus on all platforms,
    \item Runs the complete cyclus test suite, 
    \item Reports back whether the above steps succeeded or not.
\end{enumerate}

Since these steps are performed for all incoming code, it is easy for the 
cyclus core team to determine whether or not an indivudual pull request 
actually works. This helps identify build and test problems prior to 
broken code being allowed into the develop branch.

CI has become a neccessary but not sufficient addition to the cyclus QA
system. Its merit is that it keeps bad code out. However, cyclus will always
require human eyes and human hands to let good code in.
